Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
fix all longtable numbering/labeling

\begin{longtable}	{| c || c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$0$ & $\{1\}$ & $\emptyset$ \\	\hline

@@

\begin{center}
\label{table:g-1-base}
Genus 1 base cases
\end{center}

\todo{label/ref of long tables doesn't work!}

@@

\begin{longtable}	{| c || c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$P - Q$ & $\{2\}$ & $\emptyset$ \\	\hline

@@

%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
\end{longtable}
\todo{Possibly add an autoincrement counter to deal with table numbering}
\todo{label/ref of long tables doesn't work!}

\begin{center}
\label{table:g-1-exceptional}
Genus 1 exceptional cases
\end{center}

@@

\begin{longtable}
	{| c | c |}
	\hline
	Signature & Saturation \\
	\hline
	\hline

@@

\begin{center}
Genus 0 saturation \todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}
\end{center}

@@

The following table demonstrates that $R(\sx', 0, L')$ is
generated as a $k$-algebra by elements of degree at most $e$
with relations in degree at most $2e$ for each case. Also note
that in these cases, $e_i = e + 2 > \deg z$ for all $i \in J$
and any generator $z$ of $R'$.
\begin{longtable}
	{| c || c | c | c |}
	\hline
	Case & Generator Degrees & Degrees of Relations & $e$\\
	\hline
	\hline

@@

\begin{center}
Genus 0 non-effective base cases generator/relations
\end{center}

@@

\begin{longtable}
	{| c | c | c || c | c |}
	\hline
	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
	\hline
	\hline

@@

\begin{center}
Genus 0 non-effective base cases (Ad-iii)
\end{center}

@@

\begin{longtable}
	{| c || c | c | c |}
	\hline
	Signature & Generator Degrees & Degrees of Relations & $e$ \\
	\hline
	\hline

@@

\begin{center}
\label{table:g-0-exceptional}
Genus 0 exceptional cases
\end{center}

>>>>

\begin{longtable}	{| c || c | c |}
	\caption{Genus 1 Base Cases}
	\label{table:g-1-base}

	\tabularnewline

	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$0$ & $\{1\}$ & $\emptyset$ \\	\hline

@@

@@

\begin{longtable}	{| c || c | c |}
	\caption{Genus 1 Exceptional Cases}
	\label{table:g-1-exceptional}

	\tabularnewline

	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$P - Q$ & $\{2\}$ & $\emptyset$ \\	\hline

@@

@@

\begin{longtable}
	{| c | c |}
	\caption{Genus 0 Saturation}
	\label{table:g-0-sat}

	\tabularnewline

	\hline
	Signature & Saturation \\
	\hline
	\hline

@@

\todo{I see it says this above, but I think in the table, it should be made clear exactly what the hypotheses on $k,a,b,c,e_i$ are.}

@@

The following table demonstrates that $R(\sx', 0, L')$ is
generated as a $k$-algebra by elements of degree at most $e$
with relations in degree at most $2e$ for each case. Also note
that in these cases, $e_i = e + 2 > \deg z$ for all $i \in J$
and any generator $z$ of $R'$.
\begin{longtable}
	{| c || c | c | c |}
	\caption{Genus 0 Non-effective Base Cases Generators/Relations}
	\label{table:g-0-base-cases}

	\tabularnewline

	\hline
	Case & Generator Degrees & Degrees of Relations & $e$\\
	\hline
	\hline

@@

@@

\begin{longtable}
	{| c | c | c || c | c |}
	\caption{Genus 0 Non-Effective Base Cases (Ad-iii)}
	\label{table:g-0-base-cases-admissibility}

	\tabularnewline

	\hline
	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
	\hline
	\hline

@@

@@

\begin{longtable}
	{| c || c | c | c |}
	\caption{Genus 0 Exceptional Cases}
	\label{table:g-0-exceptional}

	\tabularnewline

	\hline
	Signature & Generator Degrees & Degrees of Relations & $e$ \\
	\hline
	\hline

@@
